Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-13 paper/responseToReviewers.tex

We would like to thank the editor and the reviewers for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer's comments, with references to the revised manuscript where appropriate.

\section{Responses to the Associate Editor}

\begin{enumerate}

\item \emph{Line 40, alpha may appear in previous equations}
As far as we can tell, $\alpha$ only appears during the definition of the $\widehat{\mathrm{EMD}}$ distance and not anywhere else.

\item \emph{The argumentation toward the log compression is well conducted, and meaningful in this issue. The authors may simply swap the order of fig 3 and 4}
The order of the figures and their corresponding text have been reversed.

### 2016-12-13 paper/structureScene.tex
Add discussion of odd classes

Our results on the public part of the DCASE 2016 dataset are reported in Table \ref{table:dcase2016}, compared with a baseline using MFCCs and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. This baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods. For comparison, we also provide the results for the same MFCC features coupled with a linear SVM classifier. Results here are slightly worse since the SVM can only discriminate between classes that are linearly separable, a limitation not present for the GMMs.
With the scattering transforms, however, the average accuracy across classes is brought from $70.8\%$ to $79.4\%$.\footnote{Challenge results on the private part of the dataset are expected to be published in August 2016.}
Furthermore, our cross-validation analysis confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.

>>>>

Our results on the public part of the DCASE 2016 dataset are reported in Table \ref{table:dcase2016}, compared with a baseline using MFCCs and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. This baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods. For comparison, we also provide the results for the same MFCC features coupled with a linear SVM classifier. Results here are slightly worse since the SVM can only discriminate between classes that are linearly separable, a limitation not present for the GMMs.

With the scattering transforms, however, the average accuracy across classes is brought from $70.8\%$ to $79.4\%$.\footnote{Challenge results on the private part of the dataset are expected to be published in August 2016.} It is interesting to note, however, that two classes, ``home'' and ``residential\_area'' both drop significantly in accuracy from the baseline GMM model to the scattering SVM classifier. This can be partially explained by the substitution of the GMM with an SVM, which shows a similar drop for the MFCCs. However, another reason could be that these classes are well-characterized by the average spectral envelope of the signal and the second-order modulation information captured by the scattering coefficients is therefore superfluous.
Furthermore, our cross-validation analysis confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.
